maxent model avec xvalidation (year-based test training)

### 2019-07-30 src/maxent_alldata_avec_xvalidation.Rmd
feckit

```{r final models predict}

filenames <- list.files("../data/all_data_layers/", pattern="*.csv", full.names=TRUE)
unlayer_yrX <- rbindlist(lapply(filenames,fread))
unlayer_yrX <- unlayer_yrX[complete.cases(unlayer_yrX), ]
aea <- raster("../output/env/aea.tif") 
unlayer_yr <- subset(unlayer_yrX, ascmonths == "7")

@@

      #stackSave(test,unlayer_yr$stackname[td])
      pred <- predict(mod, stack, file = paste0("../output/maxent/all_data/predictions/", "cloglog_", stackn, ".asc"), overwrite=TRUE, args='outputformat=cloglog') 
      #prplot <- plot(pred, png(paste0("../output/maxent/all_data/predictions/", "cloglog_", stackn, ".png")))
      #dev.off() # stops automatic saving of the plot to a png

@@

```{r avg asc layers cloglog}
stdep <- read.csv("../output/maxent/all_data/stackdepthlist.csv", header = TRUE)
asc_list <- list.files(paste0("../output/maxent/all_data/predictions/"), pattern = "cloglog.*.asc", full.names = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (d in 1:nrow(depthlayers)){
  dep <- depthlayers$depth[d]
  for (a in 1:length(asc_list)){
    asc <- asc_list[a]
    if (grepl(dep, asc)){
      depthlayers[d , paste0("a", colno)] <- asc
      colno <- colno+1
    }
  }
}
write.csv(depthlayers, ("../output/maxent/all_data/predictions/cloglog_asclayerbydepth.csv"), row.names = FALSE)

@@

for (x in 1:nrow(depthlayers)){
  dstack <- stack()
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  dep <- as.character(asclay[1])
  asclay <- as.data.frame(rbind(asclay))
  asclay[1] <- NULL
  for (ly in 1:length(asclay)){
    lay <- as.character(asclay[ ,40])
    layr <- raster(lay)
    dstack <- stack(dstack, layr)
    if(ly == length(asclay)){
      stavg <- calc(dstack, fun = mean, na.rm = TRUE)
      writeRaster(stavg, (paste0("../output/maxent/all_data/predictions/avg_", dep, ".asc")), overwrite=TRUE)
      avgplot <- plot(stavg, png(paste0("../output/maxent/all_data/predictions/avg_", dep, ".png")))
      while (!is.null(dev.list()))  dev.off()
    }
  }
}

@@

```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/all_data/predictions/", pattern = "binary_avg_2d.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
#brk <- seq(0.1, 1, 0.1) #for legend
redtrans <- rgb(218, 215, 216, 90, maxColorValue=255) 
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

  pras <- raster("../output/maxent/predictions/jul/binary_highavg_2d.asc")
  crs(pras) <- apr
  ascname <- names(pras)
  pras[pras >0] <- 1
  lp <- plot(pras, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = FALSE)
  lp <- plot(pras)
  lp <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp <- plot(s, col = "#474646", border = "#474646", add = TRUE)
  print(lp)
  dev.copy(png, ("../output/maxent/all_data/predictions/july/oldmod_p80_2d_july.png"), width = 1920,height = 1080)
  dev.off() # stops automatic saving of the plot to a png))
```

>>>>

```{r final models predict}
mod <- readRDS(file = "../output/maxent/all_data/maxmod.rds", refhook = NULL)
px <- response(mod@models[[4]])

filenames <- list.files("../data/all_data_layers/", pattern="*.csv", full.names=TRUE)
unlayer_yrX <- rbindlist(lapply(filenames,fread))
unlayer_yrX <- unlayer_yrX[complete.cases(unlayer_yrX), ]
aea <- raster("../output/env/aea.tif") 
unlayer_yr <- subset(unlayer_yrX, ascmonths == "11")

@@

      #stackSave(test,unlayer_yr$stackname[td])
      pred <- predict(mod, stack, file = paste0("../output/maxent/all_data/predictions/nov/", "cloglog_", stackn, ".asc"), overwrite=TRUE, args='outputformat=cloglog') 
      #prplot <- plot(pred, png(paste0("../output/maxent/all_data/predictions/", "cloglog_", stackn, ".png")))
      #dev.off() # stops automatic saving of the plot to a png

@@

```{r avg asc layers cloglog}
stdep <- read.csv("../output/maxent/all_data/stackdepthlist.csv", header = TRUE)
asc_list <- list.files(paste0("../output/maxent/all_data/predictions/nov"), pattern = "cloglog.*.asc", full.names = TRUE)
depthlayers <- data.frame(cbind(unique(stdep$ascdepths)))
names(depthlayers)[names(depthlayers) == "cbind.unique.stdep.ascdepths.."] <- "depth"
depthlayers$depth <- as.character(depthlayers$depth)

@@

for (d in 1:nrow(depthlayers)){
  dep <- depthlayers$depth[d]
  for (a in 1:length(asc_list)){
    asc <- asc_list[a]
    if (grepl(dep, asc)){
      depthlayers[d , paste0("a", colno)] <- asc
      colno <- colno+1
    }
  }
}
write.csv(depthlayers, ("../output/maxent/all_data/predictions/nov/cloglog_asclayerbydepth.csv"), row.names = FALSE)

@@

for (x in 1:nrow(depthlayers)){
  dstack <- stack()
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  dep <- as.character(asclay[1])
  asclay <- as.data.frame(rbind(asclay))
  asclay[1] <- NULL
  for (ly in 1:length(asclay)){
    lay <- as.character(asclay[ ,40])
    layr <- raster(lay)
    dstack <- stack(dstack, layr)
    if(ly == length(asclay)){
      stavg <- calc(dstack, fun = mean, na.rm = TRUE)
      writeRaster(stavg, (paste0("../output/maxent/all_data/predictions/nov/avg_", dep, ".asc")), overwrite=TRUE)
      avgplot <- plot(stavg, png(paste0("../output/maxent/all_data/predictions/nov/avg_", dep, ".png")))
      while (!is.null(dev.list()))  dev.off()
    }
  }
}

@@

```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/all_data/predictions/", pattern = "binary_avg_2d.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
#brk <- seq(0.1, 1, 0.1) #for legend
redtrans <- rgb(218, 215, 216, 90, maxColorValue=255) 
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
presback <- read.csv("../output/bio/presab_nafo_yr.csv", header = TRUE)
pronly <- subset(presback, occurrence == 1)
prjul <- subset(pronly, month == 7)
prjan <- subset(pronly, month == 1)

  pras <- raster("../output/maxent/predictions/jul/binary_highavg_2d.asc")
  crs(pras) <- apr
  ascname <- names(pras)
  pras[pras >0] <- 1
  #lp <- plot(pras, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = FALSE)
  lp <- plot(pras, axes = FALSE, box = FALSE, legend = FALSE)
  lp <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp <- plot(s, col = "#474646", border = "#474646", add = TRUE)
  lp <- points(prjul$longitude_meters, prjul$latitude_meters, add = TRUE)
  print(lp)
  dev.copy(png, ("../output/maxent/all_data/predictions/july/oldmod_p80_2d_july.png"), width = 1920,height = 1080)
  dev.off() # stops automatic saving of the plot to a png))
```
